Synthesis report

### 2020-05-07 analysis/reports/95_interval_portal.Rmd
run make all

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c() +
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()+
  facet_wrap(vars(dat), scales = "free")

@@

all_di_skew <- all_di %>%
  filter(!singletons, s0 > 2) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(skew_95_ratio)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

@@

all_di_simpson <- all_di %>%
  filter(!singletons) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(simpson_95_ratio)%>%
  mutate(ratio_rank = row_number()) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))))

@@

ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio)) +
  geom_point() +
  theme_bw()

filter(small_di, skew_95_ratio == min(small_di$skew_95_ratio, na.rm = T))

@@

ggplot(filter(di_fs_1879_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

@@

ggplot(filter(di_fs_1469_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

@@

ggplot(filter(di_fs_1218_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

>>>>

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + 
    scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t))+
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c() +
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()+
  facet_wrap(vars(dat), scales = "free")

@@

all_di_skew <- all_di %>%
  filter(!singletons, s0 > 2) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(skew_95_ratio_1t)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

@@

all_di_simpson <- all_di %>%
  filter(!singletons) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(simpson_95_ratio_1t)%>%
  mutate(ratio_rank = row_number()) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))))

@@

ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio_1t))+
  geom_point() +
  theme_bw()

filter(small_di, skew_95_ratio_1t == min(small_di$skew_95_ratio_1t, na.rm = T))

@@

ggplot(filter(di_fs_1879_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
 # geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red") +
  theme_bw()

@@

ggplot(filter(di_fs_1469_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
#  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red") +
  theme_bw()

@@

ggplot(filter(di_fs_1218_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
 # geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red") +
  theme_bw()

### 2020-05-07 analysis/reports/fia_size.Rmd
run make all

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0) %>%
  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", "fia", dat))
```

@@

ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
  geom_histogram() + theme_bw() +
  ggtitle("Skew - all sites")

@@

ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
  geom_histogram() + theme_bw() +
  ggtitle("Simpson all sites")

@@

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0) %>%
  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", "fia", dat)) %>%
  filter(dat != "portal_plants", dat != "portal_rodents")
```

@@

ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
  geom_histogram() + theme_bw() +
  ggtitle("Skew - all sites within FIA size")

@@

ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
  geom_histogram() + theme_bw() +
  ggtitle("Simpson all sites within FIA size")

@@

# Remove fia sized from all

```{r remove fia sized}

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw() +
  ggtitle("Skew - all sites larger than FIA")

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw() +
  ggtitle("Simpson - all sites larger than FIA")

ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")
```

```{r onetailed intervals}

ggplot(all_di, aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(end = .9)

ggplot(all_di, aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(end = .9)
```

### 2020-05-07 analysis/reports/fia_v_portal.Rmd
run make all

>>>>

```{r compare fia to portal rodents}

ggplot(filter(fia_sized, dat %in% c("fia", "portal_rodents")), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .3) +
  geom_point(data = filter(all_di, dat == "portal_rodents")) +
  theme_bw()

ggplot(filter(fia_sized, dat %in% c("fia", "portal_rodents"), s0 > 2), aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(dat, small_n), scales = "free_y") +
  theme_bw()

### 2020-05-07 analysis/reports/figs.Rmd
strugggles
run make all

@@

>>>>

### Remove FIA

```{r overall relationships no fia}

ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()

@@

```{r 1t hists}

ggplot(all_di_skew, aes(x = skew_95_ratio_1t))  +
geom_histogram() +   theme_bw() +
  facet_wrap(vars(nparts_rank_binned))

ggplot(all_di_skew, aes(x = skew_95_ratio_1t)) +
  geom_histogram(aes(x = skew_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
theme_bw() +
  facet_wrap(vars(nparts_rank_binned))

ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t))  +
geom_histogram() +   theme_bw() +
  facet_wrap(vars(nparts_rank_binned))

ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t)) +
  geom_histogram(aes(x = simpson_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
theme_bw() +
  facet_wrap(vars(nparts_rank_binned))
